\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-04-25 sections/supplementary.tex
Fix: Update arrangement of figures and tables for suppl

  \subsection*{Mismatches in all assignments at the \ac{TA} step}

@@

  In Table~\ref{tab:network_metrics} we show various global network metrics calculated for each tool in the pipeline.
  All the networks that make use of a particular tool are grouped together and the average metrics are calculated for each group.
  All the metrics were calculated using the \texttt{networkx} Python package~\cite{hagbergExploringNetworkStructure2008}.
  \begin{enumerate}
    \item The average shortest path length describes the average of all the shortest paths in the graph. No number is reported if the graph is not connected, thereforce, none of the networks that make use of \ac{harmonies}, \ac{cozine}, \ac{spring}, \ac{spieceasi} and Pearson are connected.
    \item The average clustering is the average clustering coefficient of the graph. The closer the value is to 1.0, the more densely connected is the graph. We can observe that the networks that use correlation-based methods have the highest values while the direct-association based methods have the lowest.
    \item The number of connected components are the highest for the direct-association based methods and the lowest for the correlation-based methods. In the case of propr, all the networks have only one giant component.
    \item Modularity metric is the average modularity over all partitions in a graph calculated using a label propagation algorithm. Positive values imply that there are more edges between vertices of the same type than we would expect by chance, and negative means that there are less. The networks inferred by \ac{mldm} report very few edges, and skew the average modularity scores.
    \item Node connectivity refers to the minimum number of nodes that must be removed from the graph to make it disconnected. We observe that only the networks generated using propr have a high value since most of these networks are connected.
    \item Edge connectivity refers to the minimum number of edges that must be removed from the graph to make it disconnected. These values are similar to node connectivity.
    \item Degree assortativity coefficient measures the similarity of connections in the graph with respect to the node degree. Again we observe that the direct-association based methods have negative degree assortativity, meaning that there are many hubs in these networks. The correlation-based methods have positive values implying that in these networks nodes with similar degrees attach to one another.
  \end{enumerate}

  \begin{table}[]

@@

    \begin{tabular}{|l|l|l|l|l|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}

@@

  DC & CC            & TA                & OP          & NI         & Average shortest path length & Average clustering & No. of connected components & Modularity & Node connectivity & Edge connectivity & Degree assortativity coefficient \\ \hline
  DB & -             & -                 & -           & -          & 2.066                        & 0.265              & 27.088                      & 0.387      & 1.868             & 1.868             & 0.070                            \\
  OR & -             & -                 & -           & -          & 1.904                        & 0.273              & 24.868                      & -17.060    & 1.877             & 1.877             & 0.099                            \\
  D2 & -             & -                 & -           & -          & 2.263                        & 0.267              & 28.228                      & 0.326      & 1.789             & 1.789             & 0.078                            \\
  DN & -             & -                 & -           & -          & 2.065                        & 0.272              & 25.132                      & 0.302      & 1.754             & 1.754             & 0.093                            \\
  CR & -             & -                 & -           & -          & 1.937                        & 0.276              & 24.289                      & -1.865     & 2.079             & 2.079             & 0.097                            \\
  -  & remove bimera & -                 & -           & -          & 2.070                        & 0.272              & 25.968                      & -7.439     & 1.863             & 1.863             & 0.086                            \\
  -  & uchime        & -                 & -           & -          & 2.066                        & 0.269              & 25.874                      & 0.275      & 1.884             & 1.884             & 0.089                            \\
  -  & -             & BLAST(NCBI)       & -           & -          & 2.218                        & 0.262              & 22.784                      & -3.683     & 1.495             & 1.495             & 0.100                            \\
  -  & -             & NaiveBayes(SILVA) & -           & -          & 1.872                        & 0.275              & 30.716                      & 0.415      & 2.674             & 2.674             & 0.074                            \\
  -  & -             & NaiveBayes(GG)    & -           & -          & 2.086                        & 0.274              & 24.263                      & -7.478     & 1.453             & 1.453             & 0.088                            \\
  -  & -             & -                 & Filter(on)  & -          & 1.975                        & 0.252              & 18.493                      & -7.194     & 1.880             & 1.880             & 0.073                            \\
  -  & -             & -                 & Filter(off) & -          & 2.193                        & 0.291              & 34.174                      & 0.431      & 1.867             & 1.867             & 0.104                            \\
  -  & -             & -                 & -           & propr      & 1.650                        & 0.528              & 1.000                       & 0.000      & 10.583            & 10.583            & 0.036                            \\
  -  & -             & -                 & -           & harmonies  &                              & 0.108              & 82.633                      & 0.757      & 0.000             & 0.000             & 0.340                            \\
  -  & -             & -                 & -           & flashweave & 3.878                        & 0.079              & 1.800                       & 0.458      & 0.383             & 0.383             & -0.032                           \\
  -  & -             & -                 & -           & cozine     &                              & 0.090              & 82.167                      & 0.694      & 0.000             & 0.000             & -0.072                           \\
  -  & -             & -                 & -           & spring     &                              & 0.092              & 11.767                      & 0.566      & 0.000             & 0.000             & -0.035                           \\
  -  & -             & -                 & -           & sparcc     & 1.747                        & 0.525              & 1.033                       & 0.009      & 5.500             & 5.500             & -0.011                           \\
  -  & -             & -                 & -           & spieceasi  &                              & 0.076              & 39.383                      & 0.717      & 0.000             & 0.000             & -0.031                           \\
  -  & -             & -                 & -           & pearson    &                              & 0.457              & 23.883                      & 0.551      & 0.000             & 0.000             & 0.478                            \\
  -  & -             & -                 & -           & spearman   & 1.875                        & 0.551              & 1.450                       & 0.044      & 1.117             & 1.117             & 0.170                            \\
  -  & -             & -                 & -           & mldm       & 2.760                        & 0.130              & 2.267                       & -75.648    & 0.433             & 0.433             & -0.028                           \\ \hline

@@

    \textbf{Table of global network metrics for all combinations of networks}.

@@

>>>>

  \subsection*{Mismatches in all assignments at the \ac{ta} step}

@@

  In Table~\ref{tab:network_metrics} we show various global network metrics calculated for each tool in the pipeline.
  All the networks that make use of a particular tool are grouped together and the average metrics are calculated for each group.
  All the metrics were calculated using the \texttt{networkx} Python package~\cite{hagbergExploringNetworkStructure2008}.
  \begin{enumerate}
    \item The average shortest path length describes the average of all the shortest paths in the graph. No number is reported if the graph is not connected, thereforce, none of the networks that make use of \ac{harmonies}, \ac{cozine}, \ac{spring}, \ac{spieceasi} and Pearson are connected.
    \item The average clustering is the average clustering coefficient of the graph. The closer the value is to 1.0, the more densely connected is the graph. We can observe that the networks that use correlation-based methods have the highest values while the direct-association based methods have the lowest.
    \item The number of connected components are the highest for the direct-association based methods and the lowest for the correlation-based methods. In the case of propr, all the networks have only one giant component.
    \item Modularity metric is the average modularity over all partitions in a graph calculated using a label propagation algorithm. Positive values imply that there are more edges between vertices of the same type than we would expect by chance, and negative means that there are less. The networks inferred by \ac{mldm} report very few edges, and skew the average modularity scores.
    \item Node connectivity refers to the minimum number of nodes that must be removed from the graph to make it disconnected. We observe that only the networks generated using propr have a high value since most of these networks are connected.
    \item Degree assortativity coefficient measures the similarity of connections in the graph with respect to the node degree. Again we observe that the direct-association based methods have negative degree assortativity, meaning that there are many hubs in these networks. The correlation-based methods have positive values implying that in these networks nodes with similar degrees attach to one another.
  \end{enumerate}

  \begin{landscape}
  \begin{table}[H]

@@

    \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{2cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|}

@@

  DC & CC            & TA                & OP          & NI         & Average shortest path length & Average clustering & No. of connected components & Modularity & Node connectivity & Degree assortativity coefficient \\ \hline
  DB & -             & -                 & -           & -          & 2.066                        & 0.265              & 27.088                      & 0.387      & 1.868             & 0.070                            \\
  OR & -             & -                 & -           & -          & 1.904                        & 0.273              & 24.868                      & -17.060    & 1.877             & 0.099                            \\
  D2 & -             & -                 & -           & -          & 2.263                        & 0.267              & 28.228                      & 0.326      & 1.789             & 0.078                            \\
  DN & -             & -                 & -           & -          & 2.065                        & 0.272              & 25.132                      & 0.302      & 1.754             & 0.093                            \\
  CR & -             & -                 & -           & -          & 1.937                        & 0.276              & 24.289                      & -1.865     & 2.079             & 0.097                            \\
  -  & remove bimera & -                 & -           & -          & 2.070                        & 0.272              & 25.968                      & -7.439     & 1.863             & 0.086                            \\
  -  & uchime        & -                 & -           & -          & 2.066                        & 0.269              & 25.874                      & 0.275      & 1.884             & 0.089                            \\
  -  & -             & NCBI              & -           & -          & 2.218                        & 0.262              & 22.784                      & -3.683     & 1.495             & 0.100                            \\
  -  & -             & SILVA             & -           & -          & 1.872                        & 0.275              & 30.716                      & 0.415      & 2.674             & 0.074                            \\
  -  & -             & GG                & -           & -          & 2.086                        & 0.274              & 24.263                      & -7.478     & 1.453             & 0.088                            \\
  -  & -             & -                 & On          & -          & 1.975                        & 0.252              & 18.493                      & -7.194     & 1.880             & 0.073                            \\
  -  & -             & -                 & Off         & -          & 2.193                        & 0.291              & 34.174                      & 0.431      & 1.867             & 0.104                            \\
  -  & -             & -                 & -           & propr      & 1.650                        & 0.528              & 1.000                       & 0.000      & 10.583            & 0.036                            \\
  -  & -             & -                 & -           & harmonies  &                              & 0.108              & 82.633                      & 0.757      & 0.000             & 0.340                            \\
  -  & -             & -                 & -           & flashweave & 3.878                        & 0.079              & 1.800                       & 0.458      & 0.383             & -0.032                           \\
  -  & -             & -                 & -           & cozine     &                              & 0.090              & 82.167                      & 0.694      & 0.000             & -0.072                           \\
  -  & -             & -                 & -           & spring     &                              & 0.092              & 11.767                      & 0.566      & 0.000             & -0.035                           \\
  -  & -             & -                 & -           & sparcc     & 1.747                        & 0.525              & 1.033                       & 0.009      & 5.500             & -0.011                           \\
  -  & -             & -                 & -           & spieceasi  &                              & 0.076              & 39.383                      & 0.717      & 0.000             & -0.031                           \\
  -  & -             & -                 & -           & pearson    &                              & 0.457              & 23.883                      & 0.551      & 0.000             & 0.478                            \\
  -  & -             & -                 & -           & spearman   & 1.875                        & 0.551              & 1.450                       & 0.044      & 1.117             & 0.170                            \\
  -  & -             & -                 & -           & mldm       & 2.760                        & 0.130              & 2.267                       & -75.648    & 0.433             & -0.028                           \\ \hline

@@

    \textbf{Table of global network metrics for all combinations of networks.}

@@

  \end{landscape}
